Speeding up eQTL scans in the BXD population using GPU

### 2019-07-26 paper.tex
Added to intro.

Compare matrix eQTL \citep{shabalin2012matrix}, GridLMM \citep{runcie2018fast}, Bolt-LMM \citep{loh2015efficient}

@@

>>>>

To perform eQTL scans in the BXD population, one has to simply perform
as many genome scans as there are phenotypes.  This can be done in an
``embarassingly parallel'' fashion by using standard algorithms for
QTL analysis, such as those employed by R/qtl (cite).  In practice,
this is too slow, and substantial speedups are possible.  [Mention
  ideas that have been used before] For example, by using the
Haley-Knott algorithms using genotype probabilities on batches of
phenotypes with the same missing data pattern, instead of using the EM
algorithm on each phenotype individually, substantial speedups are
possible.  This is a well-known trick and is used by R/qtl.
Additionally, if only additive effects are tested, or if the
population has only two genotype categories (as in a backcross or
recombinant inbred line), then matrix multiplication can be used to
perform Haley-Knott regression \citep{shabalin2012matrix}.

%% Compare matrix eQTL GridLMM \citep{runcie2018fast}, Bolt-LMM
%% \citep{loh2015efficient}

We sought to build upon these efforts aiming to perform real-time eQTL
scans for the BXD populations.  We used the above-mentioned ideas and
examined the use of graphical processing units (GPUs) to speed these
further.  Since programming for GPUs is often non-trivial needing the
use of low-level languages such as C++, we used the Julia programming
language which offers a GPU programming capabilities while retaining
the simplicity of a high-level language such as R or Matlab.  Finally,
since most phenotype-marker associations are null, we examined the
impact of storage precision, and only returning the highest
association (LOD) score for each phenotype instead of a matrix of LOD
scores for every pair of marker and phenotypes.  With these efforts,
we find that it is possible to perform perform real-time eQTL scans
for the BXD population.

@@

\subsection{BXD genotypes and phenotypes}

Describe genotype and phenotype data here.
